\hlc[green]{Uranyl Solvation by a Three-Dimensional Reference Interaction Site Model}

### 2015-06-17 doc/uo2_paper/uo2-II.tex
AM: rm redundant spaces in hlc-macro
AM: comma, word wrap

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }
\usepackage{mathptmx}
\usepackage{times}
%\usepackage{microtype}
%\def\thetable{\arabic{table}}
%\usepackage{ragged2e}
%\usepackage[textfont=it]{caption}
\captionsetup{font={bf}}

@@

\begin{figure}[tbph]
\caption{Radial distribution functions of solvated uranyl without explicit
aqua ligands: U--O$_{\text{w}}$ (top panel, \hlc[green]{red}), U--H$_{\text{w}}$
(top panel, \hlc[green]{blue}), O--O$_{\text{w}}$ (bottom panel, \hlc[green]{red}) and O--H$\text{\ensuremath{_{w}}}$ (bottom panel, \hlc[green]{blue}). Results obtained with the PSE1 closure are shown
as \hlc[green]{solid lines}, results obtained with the closure relations PSE2 and PSE3 are displayed \hlc[green]{using dashed lines and dotted lines respectively}.  \label{fig:rdfs-vs-closure-0w}}

@@

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3, \hlc[green]{are displayed as solid, dashed and dot-dashed lines respectively}. The \hlc[green]{dotted} line
represents the MD result of Ref.~\citenum{Bo15}.
\label{fig:potential-of-mean-force}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
\usepackage{mathptmx}
\usepackage{times}
%\usepackage{microtype}
%\def\thetable{\arabic{table}}
%\usepackage{ragged2e}
%\usepackage[textfont=it]{caption}
\captionsetup{font={bf}}

@@

\begin{figure}[tbph]

\caption{Radial distribution functions of solvated uranyl without
  explicit aqua ligands: U--O$_{\text{w}}$ (top panel,
  \hlc[green]{red}), U--H$_{\text{w}}$ (top panel, \hlc[green]{blue}),
  O--O$_{\text{w}}$ (bottom panel, \hlc[green]{red}) and
  O--H$\text{\ensuremath{_{w}}}$ (bottom panel,
  \hlc[green]{blue}). Results obtained with the PSE1 closure are shown
  as \hlc[green]{solid lines}, results obtained with the closure
  relations PSE2 and PSE3 are displayed \hlc[green]{using dashed lines
    and dotted lines respectively}.  \label{fig:rdfs-vs-closure-0w}}

@@

\begin{figure}[tbph]
\begin{centering}

\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$
  radial distribution function, determined with the closure relations
  PSE1, PSE2 and PSE3, \hlc[green]{are displayed as solid, dashed and
  dot-dashed lines, respectively}. The \hlc[green]{dotted} line
  represents the MD result of Ref.~\citenum{Bo15}.
\label{fig:potential-of-mean-force}}
